---
title: "Forest plots of country-specific estimates"
author: "Andrew Mertens"
output:
  html_document:
    df_print: paged
  word_document:
    reference_docx: MICS_WASH_BOD_analysis_plan.docx
---

<!-- output: html_notebook -->
<!-- editor_options:  -->
<!--   chunk_output_type: inline -->



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1) 
library(janitor)
library(knitr)
library(here)
library(table1)
library(rvest)

source(here("0-config.R"))


op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
 library(pander)
panderOptions('digits', 2)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('graph.fontsize', 8)

panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)


plist <- readRDS(here("figures/forest_figure_objects.rds"))


```



_Figure details for all plots:_ Each plot shows country-specific and pooled estimates for each WASH characteristic-outcome combination (printed in each figure title). All estimates are adjusted for potential confounders. Sample size for each estimate are in parentheses. Multi-panel figures compare categories of WASH characteristics (printed at the top of each panel) to the most-improved reference level (printed after `ref=` in the X-axis label). Points are colored by the MICS region, with pooled estimates in black, and labeled as pooled estimates from random effects (RE) or fixed effects (FE) models.


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 5}
#for(i in 1:4){
for(i in 1:length(plist)){
  print(plist[[i]])
}


```